Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
minor fixes

This section presents our second contribution, a space-efficient CEK abstract 
machine. This machine is parameterized over \emph{cast representation} (CR).

@@

% Did you really mean to delete all the following? -Jeremy
%% With the properties of surely \lazyD{} CR, it is straightforward to proof that 
%% all machines instantiated with these CRs bisimulate each other. 
%% The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
%% derived from the definition of states.
%% \todo[inline]{The term ``bisimilarity'' has a different technical meaning from
%%   ``bisimulation relation''. I don't think you are using it properly
%%   in the above sentence. -Jeremy}
%% We omit subscripts when there is no 
%% ambiguity.
%% \begin{gather*}
%% \inference{
%% 	\rho_1 \approx \rho_2 &
%% 	\kappa_1 \approx \kappa_2
%% }{
%% 	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
%% }
%% \quad
%% \inference{
%% 	\kappa_1 \approx \kappa_2 &
%% 	v_1 \approx v_2
%% }{
%% 	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
%% }
%% \quad
%% \inference{
%% }{
%% 	\sOOhalt{o} \approx \sOOhalt{o}
%% }
%% \end{gather*}

%% The relations between continuations, pre-continuations, enviroments, values, 
%% cast results are also derived from their definitions. But the relation for 
%% casts is special: \begin{gather*}
%% \inference{
%% }{
%% 	cast_1(T_1,l,T_2) \approx cast_2(T_1,l,T_2)
%% }
%% \quad
%% \inference{
%% }{
%% 	id_1(T) \approx id_2(T)
%% }
%% \quad
%% \inference{
%% 	c_1 \approx c_2 &
%% 	c_3 \approx c_4
%% }{
%% 	seq_1(c_1,c_3) \approx seq_2(c_2,c_4)
%% }
%% \end{gather*}

%% \begin{proposition}[Strong bisimulation among $ \mathcal{S}(\cdot) $]
%% 	\label{thm:CEKS-bisim}
%% 	If 
%% 	$ C_1 $ and $ C_2 $ are surely \lazyD,
%% 	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
%% 	$ s_1 \approx s_3 $,
%% 	$ \judgeSreduce{C_1}{s_1}{s_2} $,
%% 	then there exists an $ s_4 $ such that
%% 	\begin{itemize}
%% 	\item $ s_2 \approx s_4 $ and
%% 	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
%% 	\end{itemize}
%% \end{proposition}
%% \begin{proof}
%% 	The key ideas of this proof are undoing sequencing with the property (2) of 
%% 	surely \lazyD{} CR, and handling all possibly uses of $ 
%% 	cast(T,l,T) $ with property (3)-(11).
%% \end{proof}

%% \begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
%% 	\label{thm:surely-lazyD-eqv}
%% 	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
%% 	are surely \lazyD cast representations,
%% 	\[
%% 	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
%% 	e \Downarrow_{S(C_2)} o
%% 	\]
%% \end{proposition}
%% \begin{proof}
%% 	Immediately from Proposition~\ref{thm:CEKS-bisim}.
%% \end{proof}

%% \subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}

%% So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
%% each other. But this does not mean they respect the semantics of the \lazyD{} 
%% Blame Calculus. We solve prove this part in this subsection.

%% The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the

@@

With the properties of surely \lazyD{} CR, it is straightforward to proof that 
all machines instantiated with these CRs bisimulate each other. 
The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states.
\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
	``bisimulation relation''. I don't think you are using it properly
	in the above sentence. -Jeremy}
We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

@@

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
	$ s_1 \approx s_3 $,
	$ \judgeSreduce{C_1}{s_1}{s_2} $,
	then there exists an $ s_4 $ such that
	\begin{itemize}
	\item $ s_2 \approx s_4 $ and
	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{lemma}
\begin{proof}
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} CR, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

>>>>

This section presents our second contribution, a space-efficient CEK abstract 
machine. This machine is parameterized over \emph{cast representation}.

@@

@@

With the properties of surely \lazyD{} cast representation, it is 
straightforward to proof that 
all machines instantiated with these cast representations bisimulate each 
other. 
The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states.
\todo[inline]{The term ``bisimilarity'' has a different technical meaning from
	``bisimulation relation''. I don't think you are using it properly
	in the above sentence. -Jeremy}
We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

@@

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
	$ s_1 \approx s_3 $,
	$ \judgeSreduce{C_1}{s_1}{s_2} $,
	then there exists an $ s_4 $ such that
	\begin{itemize}
	\item $ s_2 \approx s_4 $ and
	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{lemma}
\begin{proof}
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} cast representation, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}
